Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-05 astronum_2017/astronum-amrex.tex
acks

\maestro\ and \castro\ share the same microphysics, available as the
\starkiller\ astrophysics github
project\footnote{\url{https://github.com/StarKiller-astro/microphysics/}}.
This includes equations of state and nuclear reaction networks.  The
reaction networks are written such that that rates and integration
strategy are decoupled, allowing us to change the integration strategy
for a set of rates.

@@

\ack The work at Stony Brook was supported by DOE/Office of Nuclear
Physics grant DE-FG02-87ER40317 and NSF award AST-1211563.  An award
of computer time was provided by the Innovative and Novel
Computational Impact on Theory and Experiment (INCITE) program.  This
research used resources of the Oak Ridge Leadership Computing Facility
at the Oak Ridge National Laboratory, which is supported by the Office
of Science of the U.S. Department of Energy under Contract
No.\ DE-AC05-00OR22725.  We appreciate the efforts of the OLCF (and in
particular Fernanda Foertter) in organizing the GPU hackathons.  This
research used resources of the National Energy Research Scientific
Computing Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No.\ DE-AC02-05CH11231.
Results in this paper were obtained using the high-performance LIred
computing system at the Institute for Advanced Computational Science
at Stony Brook University, which was obtained through the Empire State
Development grant NYS \#28451.  The GPU work benefited from a grant of
an Titan X Pascal board from Nvidia Corp through the GPU Grant
Program.

>>>>

\maestro\ and \castro\ share the same microphysics, available as the
\starkiller\ astrophysics github
project\footnote{\url{https://github.com/StarKiller-astro/microphysics/}}.
This includes equations of state and nuclear reaction
networks\footnote{Several of the reaction network righthand sides and
  the EOS were provided from Frank Timmes' {\em cococubed} software
  instruments page
  \url{http://cococubed.asu.edu/code_pages/codes.shtml}.  We thank him
  for making them available.}.  The reaction networks are written such
that that rates and integration strategy are decoupled, allowing us to
change the integration strategy for a set of rates.  They are also
written to be threadsafe and with GPUs in mind (more on that
below).  The goal of \starkiller\ is to evolve the code so that it is
able to be used in a variety of nuclear astrophysics codes, not just
those discussed here.

@@

\ack The work at Stony Brook was supported by DOE/Office of Nuclear
Physics grant DE-FG02-87ER40317 and NSF award AST-1211563.  An award
of computer time was provided by the Innovative and Novel
Computational Impact on Theory and Experiment (INCITE) program.  This
research used resources of the Oak Ridge Leadership Computing Facility
at the Oak Ridge National Laboratory, which is supported by the Office
of Science of the U.S. Department of Energy under Contract
No.\ DE-AC05-00OR22725.  We appreciate the efforts of the OLCF (and in
particular Fernanda Foertter) in organizing the GPU hackathons.  This
research used resources of the National Energy Research Scientific
Computing Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No.\ DE-AC02-05CH11231.
Results in this paper were obtained using the high-performance LIred
computing system at the Institute for Advanced Computational Science
at Stony Brook University, which was obtained through the Empire State
Development grant NYS \#28451.  The GPU work benefited from a grant of
an Titan X Pascal board from Nvidia Corp through the GPU Grant
Program.  This research has made use of NASA's Astrophysics Data
System Bibliographic Services.
